%% Example CV - Minh Duong
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% SETUP: Run /setup to populate this with your actual information.
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Minh Duong - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Minh}{Duong}
\address{Ho Chi Minh City, Vietnam}{}{}
\phone[mobile]{0337630099}
\email{johncegom2013@gmail.com}
\extrainfo{\href{https://linkedin.com/in/minh-duong-saiko}{LinkedIn} \textbullet{} \href{https://github.com/johncegom}{GitHub} \textbullet{} \href{https://minhduong.vercel.app}{Portfolio}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{-10pt}
\small{Software Engineer with over 4 years of experience building high-availability telecommunications solutions and network-connected mobile platforms. Proven expertise in developing real-time communication backends using Erlang and designing BLE/Wi-Fi communication layers in React Native. Certified Scrum Master experienced in leading lean engineering teams to deliver stable, high-quality software architectures.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Programming Languages}: Go, Erlang, TypeScript, JavaScript, SQL

\item \textbf{Frameworks \& Libraries}: React Native, React, Redux, Redux Toolkit, React Navigation, Async Storage

\item \textbf{Network \& Protocols}: SIP, Diameter, Megaco, Bluetooth Low Energy (BLE), Wi-Fi, RESTful APIs

\item \textbf{Databases}: Mnesia, SQLite, Firebase

\item \textbf{Tools \& Methods}: Git, GitLab, Jira, Gerrit, Jenkins, Confluence, Linux, Scrum/Agile

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Endava ---
\item{\cventry{July 2024--Present}{Developer / React Native Developer}{Endava Vietnam}{Ho Chi Minh City, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Contributed to a mobile platform (August 2025--July 2026) for installing, configuring, and managing industrial devices via wireless communication protocols.
    \item Optimized Bluetooth Low Energy (BLE) and Wi-Fi hardware connectivity layers, ensuring robust real-time device interaction in challenging field environments.
    \item Engineered new features and resolved critical connectivity defects, maintaining high application availability for technical operators.
    \item Collaborated in a lean, 2-person development team across the full product lifecycle from scoping to release.
\end{itemize}}}

\vspace{3pt}

% --- DEK Tech Telecom ---
\item{\cventry{July 2020--July 2024}{Telecommunications Software Engineer}{DEK Technologies}{Ho Chi Minh City, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Contributed to the development and enhancement of a high-availability Session Border Gateway/Controller telecom solution.
    \item Designed and implemented core signaling features managing communication flows using Erlang.
    \item Built and tested integration layers using SIP, Diameter, and Megaco protocols in real-time environments.
    \item Defined comprehensive test automation strategies and coverage matrices, reducing critical production bugs.
    \item Mentored and supported onboarding for new engineers to boost team productivity.
\end{itemize}}}

\vspace{3pt}

% --- DEK Tech Scrum Master ---
\item{\cventry{October 2022--October 2023}{Scrum Master}{DEK Technologies}{Ho Chi Minh City, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Led a 5-person engineering team to adopt agile principles, facilitating sprint planning, standups, and retrospectives.
    \item Established Jira workflows and metrics to distribute workload evenly and eliminate delivery bottlenecks.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2016--2021}{Engineer's degree in Information Technology}{Can Tho University}{Can Tho, Vietnam}{}{\vspace{1pt}
High Quality Program. Focused on software engineering, network programming, and databases.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Vietnamese (Native), English (Professional Working Proficiency).
\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Action Learning Foundation} -- actionlearningcoach.org (completed September 2023)
\item \textbf{Agile Crash Course} -- yesieducation.com (completed September 2023)
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
